---
title: "Homework 1 zz2901"
output: github_document
---

```{r load_package, echo = FALSE, message=FALSE}
library(tidyverse)
```

## Problem 1

### Code for loading "`penguins`" dataset and descriptions 

```{r penguins_import}
data("penguins", package = "palmerpenguins")
penguins
```

### Description for "`penguins`" dataset

* The "`penguins`" dataset has variables **`r paste0('"',colnames(penguins),'"')`**. Variable types include **factors** ("species", "island", "sex"), **doubles** ("bill_length_mm", "bill_depth_mm"), and **integers** ("flipper_length_mm", "body_mass_g", "year").  

* There are **`r nrow(penguins)` rows and `r ncol(penguins)` columns** in the dataset.

* After removing missing data, the **mean flipper length is `r round(mean(penguins$flipper_length_mm,na.rm = TRUE),digits=3)` mm**.

### Scatterplot for `flipper_length_mm` (y) vs `bill_length_mm` (x)
```{r flipper_bill_scatterplot}
plot_df <- tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm
)

ggplot(plot_df, aes(x = x, y = y, color = penguins$species)) + geom_point()
ggsave("scatter_plot_flipper_vs_bill_length.pdf")
```


