---
title: "Homework 1 zz2901"
output: github_document
---

```{r load_package, echo = FALSE, message=FALSE}
library(tidyverse)
```

## Problem 1

### Code for loading "`penguins`" dataset and descriptions 

```{r penguins_import}
data("penguins", package = "palmerpenguins")
penguins
```

### Description for "`penguins`" dataset

* The "`penguins`" dataset has variables **`r paste0('"',colnames(penguins),'"')`**. Variable types include **factors** ("species", "island", "sex"), **doubles** ("bill_length_mm", "bill_depth_mm"), and **integers** ("flipper_length_mm", "body_mass_g", "year").  

* There are **`r nrow(penguins)` rows and `r ncol(penguins)` columns** in the dataset.

* After removing missing data, the **mean flipper length is `r round(mean(penguins$flipper_length_mm,na.rm = TRUE),digits=3)` mm**.

### Scatterplot for `flipper_length_mm` (y) vs `bill_length_mm` (x)
```{r flipper_bill_scatterplot}
plot_df <- tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm
)

ggplot(plot_df, aes(x = x, y = y, color = penguins$species)) + geom_point()
ggsave("scatter_plot_flipper_vs_bill_length.pdf")
```

## Problem 2

### Create requested data frame `mean_df` and take mean of each variable

```{r mean_df}
mean_df <- tibble(
  random_sample = rnorm(10),
  logical_vector = random_sample>0,
  character_vector = c("v1","v2","v3","v4","v5","v6","v7","v8","v9","v10"),
  factor_vector = factor(c("level_1","level_1","level_1","level_1","level_1","level_1",
                           "level_1","level_1","level_2","level_3"))
)
mean_df
mean(mean_df$random_sample)
mean(mean_df$logical_vector)
mean(mean_df$character_vector)
mean(mean_df$factor_vector)
```

We could calculate the means for `random_sample` and `logical_vector`. 

But we could not calculate the means for `character_vector` or `factor_vector`.

```{r}

```

